full title

### 2020-11-21 paper/pldi21/implementation.tex
Removed inred
New one

\paragraph{Termination.}
To guarantee the termination of static analysis using dynamic shortcuts, the
filter $\checker$ should pass a state $\symbst$ only when it terminates in a
bound time $N$.  Since statically checking the termination property is a difficult task,
we simply perform sealed symbolic execution with a pre-determined time limit.  When it runs
over the time limit, we treat it as a failure to pass $\checker$; otherwise, we use
the result of sealed symbolic execution.  Our experiments used 5 seconds 
as the time limit for each sealed symbolic execution.

% \paragraph{Function-Level Dynamic Shortcut.}
% The dynamic shortcut is activated when the current abstract state passes the
% filter $\checker$.  If the filter tolerantly admits the dynamic shortcut, the
% analysis suffers from the frequent communication between static and dynamic
% analyzers.  To diminish the burden of communication, we only activate new
% dynamic shortcut in function entries thus $\tool$ supports only
% \textit{function-level} dynamic shortcut.  Moreover, the filter $\checker$
% should pass only when the given abstract state terminates in a bound time.
% Since it is difficult to staticaly check its termination, we just performs the
% sealed symbolic exeuction with a time limit and we use \inred{5} minutes time
% limit for experiments.  Thus, a sealed symbolic execution introduced by a
% function \jscode{f} terminates when it 1) meets the exit of the function
% \jscode{f}, 2) accesses the inside of sealed symbolic values, or 3) runs over
% the time limit.

>>>>

\paragraph{Termination.}
To guarantee the termination of static analysis using dynamic shortcuts, the
converter $\asconverter$ should pass an analysis element $(\view, \abselem)$
only when it terminates in a bound time $N$.  Since statically checking the
termination property is a difficult task, we simply perform sealed symbolic
execution with a pre-determined time limit.  When it runs over the time limit,
we treat it as a failure to convert the analysis element via $\asconverter$;
otherwise, we use the result of sealed symbolic execution.  Our experiments used
5 seconds as the time limit for each sealed symbolic execution.

% \paragraph{Function-Level Dynamic Shortcut.}
% The dynamic shortcut is activated when the current abstract state passes the
% filter $\checker$.  If the filter tolerantly admits the dynamic shortcut, the
% analysis suffers from the frequent communication between static and dynamic
% analyzers.  To diminish the burden of communication, we only activate new
% dynamic shortcut in function entries thus $\tool$ supports only
% \textit{function-level} dynamic shortcut.  Moreover, the filter $\checker$
% should pass only when the given abstract state terminates in a bound time.
% Since it is difficult to staticaly check its termination, we just performs the
% sealed symbolic exeuction with a time limit and we use 5 minutes time
% limit for experiments.  Thus, a sealed symbolic execution introduced by a
% function \jscode{f} terminates when it 1) meets the exit of the function
% \jscode{f}, 2) accesses the inside of sealed symbolic values, or 3) runs over
% the time limit.
